### 2016-11-05 introduction.tex
more shit

We observed copious evidence of this phenomenon in our experiments, and this is the motivation behind our decision to evaluate our pruning algorithms on the simple criteria of their ability to trim neurons \textit{without} any re-training. If we were to employ re-training as part of our evaluation criteria, we would arguably \textit{not} be evaluating the quality of our algorithm's pruning decisions per se but rather the ability of back-propagation trained networks to recover from faults caused by non-ideal pruning decisions, as suggested by the conclusions of \cite{segee1991fault} and \cite{mozer1989skeletonization}. Moreover, as \cite{fahlman1989cascade} discuss, the ``herd effect'' and ``moving target'' phenomena in back-propagation learning will simply cause the remaining units in a network to shift course to account for whatever error signal is re-introduced as a result of a bad pruning decision or network fault. So long as there are enough critical parameters to learn the function in question, a network can almost always recover with additional training. This limits the conclusions we can draw about the quality of our pruning criteria when we employ re-training.

>>>>

We observed copious evidence of this phenomenon in our experiments, and this is the motivation behind our decision to evaluate the pruning algorithms in this study on the simple criteria of their ability to trim neurons \textit{without} any re-training. If we were to employ re-training as part of our evaluation criteria, we would arguably \textit{not} be evaluating the quality of our algorithm's pruning decisions per se but rather the ability of back-propagation trained networks to recover from faults caused by non-ideal pruning decisions, as suggested by the conclusions of \cite{segee1991fault} and \cite{mozer1989skeletonization}. Moreover, as \cite{fahlman1989cascade} discuss, due to the ``herd effect'' and ``moving target'' phenomena in back-propagation learning, the remaining units in a network will simply shift course to account for whatever error signal is re-introduced as a result of a bad pruning decision or network fault. So long as there are enough critical parameters to learn the function in question, a network can typically recover with additional training. This limits the conclusions we can draw about the quality of our pruning criteria when we employ re-training.
